---
title: "Fastfood Restaurants"
output: html_notebook
---

Looking only at Burger King and Chick-Fil-A, which item has the highest calories?

```{r}
# Filtered by Burger King and Chick Fil-A, then grouped by item and sorted from highest to lowest amount of calories in each item, and selected the highest caloric food item.

Q1 <- fastfood %>% 
  filter(restaurant %in% c('Burger King', 'Chick Fil-A')) %>%  
  group_by(item) %>% 
  arrange(desc(calories)) %>% 
  select(item) %>% 
  head(1)
  
```

What is the mean sugar amount for all items from Subway?
```{r}
# Filtered by Subway and performed a statistical analysis to get the mean of sugar.

Q2 <- fastfood %>% 
  filter(restaurant == 'Subway') %>% 
  summarize(mean_sugar = mean(sugar)) %>% 
  select(mean_sugar) %>% 
  as.data.frame()
```


What is the mean value of calories for all items from Taco Bell?  
```{r}
# Filtered by Taco Bell and performed a statistical analysis to get the mean of calories.

Q3 <- fastfood %>% 
  filter(restaurant == 'Taco Bell') %>% 
  summarize(mean_calories = mean(calories)) %>% 
  select(mean_calories) %>% 
  as.data.frame()
```


Create a variable equal to total_fat x sugar called fatXsugar.  Produce a tibble that has the restaurant, item, and fatXsugar for the top 3 items, from highest to lowest.
```{r}
# Created a variable called fatXsugar using total_fat times sugar and sorted it from highest to lowest and viewed the top 3 items that have the highest fat*sugar.

Q4 <- fastfood %>% 
  mutate(fatXsugar = total_fat * sugar) %>% 
  arrange(desc(fatXsugar)) %>% 
  select(restaurant, item, fatXsugar) %>% 
  head(3)
```


How many restaurants have an average saturated fat over 10?
```{r}
# Started off by grouping by restaurant and performed a statistical analysis to get the mean of saturated fat and filter by average fat > 10. Used nrow() to see the number of restaurants that have an average saturated fat of over 10.

Q5 <- fastfood %>% 
  group_by(restaurant) %>% 
  summarize(avg_sat = mean(sat_fat)) %>% 
  filter(avg_sat > 10) %>% 
  nrow()
```


